???

### 2017-01-26 docs/language_constraint.tex

the reminder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
We present our model and our experiments at sections \ref{ssec:Model} and \ref{ssec:Experiments} respectively.
Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
We conclude at \secref{Conclusion}.

\isection{The Cloze Story Task}{ROC_Story}
\roy{High level on first paragraph: much better, but still not enough connection to our story. You need to be explicit as to why we chose this task. 
Our work is currently not mentioned at all}
Writing tasks are plentiful on Amazon Mechanical Turk (AMT) \ms{cite various examples?}\roy{I would not start with AMT, as it is not important to our discussion. Think of the message that a first sentence in a paragraph gives: this is the topic/main focus of this paragraph. AMT is only a technical detail that should be mentioned later}. As a testbed for our analyses, we \royb{chose}{focus on} the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}, during which\roy{not sure ``during which'' is right here. consider rephrasing} workers were asked to write intuitive and counter-intuitive endings to short stories. 
This task is particularly interesting in that the two endings were written by the same author, for the same story, allowing for careful comparison.\roy{This is indeed particularly interesting {\bf for us}, but currently this is out of context. I would say that this task has a few interesting properties that we exploit.}

Originally, the task was developed as an effort to facilitate representation and learning of commonsense knowledge. For that purpose, the creators crowdsourced the creation\roy{Don't use ``creators \dots creation''. Regardless, {\it creators} is not the right word here} of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
%\roy{Not sure that this sentence is so terrible, but I would not put the focus on the shared task. This is a rather minor detail and has very little relevance to our story. Think about what we want to reader who has very little time or energy to know. Specifically, I would start with few very general details and motivation (as you did), but then directly move to mention the interesting design decisions they took, which actually raise  very different type of research questions, which we tackle in this paper. Then you can move to describe it more formally, as you do below (you can mention the shared task there if you want, not sure it's even necessary).} % this is a terrible sentence.

\paragraph{ROC Stories}
consist of $98,163$\roy{Minor, but still: writing the number inside dollar signs adds a white space in the pdf. This is a bit annoying, and also potentially confusing, as in the next case you use it below (3,744 something)}  five-sentence commonsense stories, collected on AMT. Workers were instructed to write a coherent story where something happens, and with\roy{``and with'' doesn't sound right here. rephrase} a clear beginning and end. To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories.
\paragraph{Story Cloze}\roy{say something general first before diving into details} test sets were created on AMT, using a subset of ROC Stories. Presented with the first four sentences of a story, workers were asked to write a ``right'' and a ``wrong'' ending. Both endings had to complete the story using \royb{a character}{one of the characters} in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.

The resulting stories, matched with each ending, were then individually rated for coherence and meaningfulness by AMT workers. Only stories rated as simultaneaously coherent with ``right'' ending and neutral with a ``wrong'' ending were selected for the test, yielding $3,744$ test stories. It is worth noting that workers rated the stories as a whole, not the endings; no selection was done on the endings alone.
%\ms{Hope the ``neutral'' thing makes sense, I didn't know how else to explain 4.2.2 of the Story cloze paper.}\roy{Reading 4.2.2, it seems that they were not targeting badly phrased ``wrong'' sentences, but just the stories as a whole, and validated that all ``right'' stories were valid and all ``wrong'' stories were invalid (unless this is how you read the -1 option in their description, which is not addressed anywhere else in the text). If I am correct, I would write this and explicitly mention that no validation was performed on the ending level.}
\roy{Other things to talk about (not necessarily in that order): 
1. no training corpus for the task. That is, the training set (a) does not contain negative example (just positive), and (b) was not generated in the same way as the positive test samples. Here you need to explicitly say that we show that we show that the training and test sets use very different styles.
2. Maybe talk about the shared task, as well as their RepEval paper, which suggested this task as a vector-space evaluation measure?
3. Say that the authors did an extensive work in order to  assure that the positive and negative samples are not easily distinguishable: for each pair, both endings were written by the same author (you addressed this earlier, but this seems like a better location), they tried an extensive set of baselines, showing all don't surpass a random baseline by much. Maybe now you can briefly mention the benchmarks, saying that several baselines were presented in the papers. All benchmarks attempted to learn the connection between the previous paragraph and the ending, and all performed near chance level.. However, no baseline looked at the endings independently. 
Then you can add the benchmark text below, and conclude that this indicates that this task is well designed and hard and the one hand, but might also point to potential disagreements between the train and the test data, which we highlight in this paper.}

\paragraph{Benchmarks}
~\ms{Like you said, maybe this belongs in related work, but for now I'll put it here}
The creators of the dataset implemented various benchmarks, using surface level features as well as narrative informed ones. Compared to similar tasks \cite{CNN, SQUAD, SNLI}, the baselines perform relatively poorly, indicating that the task is a relatively hard one. 
%\roy{The following might belong in the related work section, but probably more relevant here: I would add a section about performance on this task, stating that the authors tried quite a few baselines and showed that all pretty much fail on the task, and other than that there was just one paper that got slightly better results. This is a place to make two more arguments:  (a) the low results obtained by the various baseline methods, as well as the low number of works (only one) that improved results on this task, compared to other similar tasks published in recent years (SQUAD, SNLI, CNN/Daily Mail., etc.), indicate that this is task is relatively hard, even for machine reading systems that has made a huge progress in recent years. (b) To the best of our knowledge, this is the first work to consider the style differences between the two endings, rather than the setup suggested by the author. \\ Btw, this could be a good place to mention the shared task.}

@@

\paragraph{Neural Language Model.}
~\ms{This needs to be placed somewhere else LOL}
~\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}
%\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good. What I'm missing here are (a) an introductory 1-2  sentences to what are we doing here (I realize that it is not 100\% clear from the intro what is the role of these experiments other than showing that we have STOA results, so this can come later\\
%(b) A one-sentence description of your model. Currently, there is no clear separation between the model (RNN using LSTM) and the technical details. 
%Some general description of the model, and specifically the motivation behind (nothing fancy, just saying that we applied state-of-the-art LM tools, 
%which resemble the tools the authors had in mind when they designed the task).}

To leverage the genre of these short stories,\roy{Not sure this is the best introductory sentence, but you can leave it to me if you can't find anything better} we train a recurrent language model (RLM) \cite{mikolov2010recurrent},\roy{don't start with the details, but with the high level. We wanted wether our model can be combined with state-of-the-art text comprehension models, for which this task was designed. {\bf Specifically}, we train an RLM \dots}  which are used to achieve state-of-the-art performance on various tasks (e.g. machine translation)\roy{citation required}. 
Training this RLM on the ROC stories, we harness the unsupervised, single-ended stories\roy{I would frame it differently. Unlike the model suggested in this paper, which only considers the endings, this model harnesses the training set as intended by the authors, which is composed of unsupervised, single-ended stories}, which boosts performance on the Story Cloze task.\roy{In what sense does it boost performance? we get STOA results without it...}

@@

% Eval
On its own, our neural language model performs moderately on the Story Cloze test. As hinted at by the creators of this task, simple language models aren't enough to do well. In fact, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55\%$ accuracy. When using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, we obtain $68\%$.\roy{(see \tabref{cloze_results}). also, its 68.1, isn't it? (just to be consistent with the table)} This doesn't beat reported SOTA\roy{SOTA is not a standard abbreviation. Use state-of-the-art}, which is why we included these features into our stylistic driven model.\roy{no, this is not why we include these as features (at least not in this paper:). It's because we want to see whether the different approaches are complementary.}\roy{Now you need to discuss our results and what they mean. You can point to \tabref{cloze_results}}

>>>>

The remainder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
We present our model and our experiments at sections \ref{ssec:Model} and \ref{ssec:Experiments} respectively.
Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
We conclude at \secref{Conclusion}.

\isection{The Cloze Story Task}{ROC_Story}
%\roy{High level on first paragraph: much better, but still not enough connection to our story. You need to be explicit as to why we chose this task. Our work is currently not mentioned at all}
To understand how constrained writing affects writing style, we focus on the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}. We exploit various interesting properties of the associated dataset and achieve state-of-the-art performance on the task.

Originally, the task was developed as an effort to facilitate representation and learning of commonsense knowledge. For that purpose, \citet{Mostafazadeh:2016} crowdsourced the collection of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.

\paragraph{ROC Stories}
consist of $98,163$ % \roy{Minor, but still: writing the number inside dollar signs adds a white space in the pdf. This is a bit annoying, and also potentially confusing, as in the next case you use it below (3,744 something)}
five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT). Workers were instructed to write a coherent story where something happens, and with%\roy{``and with'' doesn't sound right here. rephrase}
a clear beginning and end. To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories.
\paragraph{Story Cloze}%\roy{say something general first before diving into details} 
test sets consist of $3,744$ short stories, each with one ``right'' and one ``wrong'' ending, also collected on AMT.
Presented with the first four sentences of a ROC story, workers were asked to write a ``right'' and a ``wrong'' ending. Both endings had to complete the story using one of the characters in it, and when read out of context, the ending had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.

The resulting stories, matched with each ending, were then individually rated for coherence and meaningfulness by AMT workers. Only stories rated as simultaneaously coherent with a ``right'' ending and neutral with a ``wrong'' ending were selected for the test. It is worth noting that workers rated the stories as a whole, not the endings; no selection was done on the endings alone.

\paragraph{Design.}
In this task, training (ROC Stories) and test (Story Cloze) data were created differently.
%The task was designed such that the ROC stories would be used as training data and the Story Cloze stories as validation and test sets, i.e. the training and test data were created differently. 
The ROC Stories were written by one author, and only have one ``right'' ending, whereas the Story Cloze stories have two endings, neither or which were written by the author of the rest of the story. Furthermore, \citet{Mostafazadeh:2016} made sure the Story Cloze endings would be hard to distinguish automatically, as each pair of endings was written by the same author. We show that, as a result of these design choices, the style of the ROC stories is rather different from the Story Cloze stories.

\paragraph{Benchmarks.} While the Story Cloze test is now the LSDSem `17 Shared Task and was proposed as a testbed for vector-space evaluation \cite{mostafazadeh2016story}, reported performance isn't far from a random baseline. \citet{Mostafazadeh:2016} implemented various benchmarks trained on the ROC Stories, using surface level features as well as narrative-informed ones. Compared to similar tasks \cite{hermann2015teaching,rajpurkar2016squad,bowman2015large}, the benchmarks perform relatively poorly, indicating that high performance is hard to achieve.
To the best of our knowledge, no training has been done on pairs of endings.

%\roy{Other things to talk about (not necessarily in that order): 
%1. no training corpus for the task. That is, the training set (a) does not contain negative example (just positive), and (b) was not generated in the same way as the positive test samples. Here you need to explicitly say that we show that we show that the training and test sets use very different styles.
%2. Maybe talk about the shared task, as well as their RepEval paper, which suggested this task as a vector-space evaluation measure?
%3. Say that the authors did an extensive work in order to  assure that the positive and negative samples are not easily distinguishable: for each pair, both endings were written by the same author (you addressed this earlier, but this seems like a better location), they tried an extensive set of baselines, showing all don't surpass a random baseline by much. Maybe now you can briefly mention the benchmarks, saying that several baselines were presented in the papers. All benchmarks attempted to learn the connection between the previous paragraph and the ending, and all performed near chance level.. However, no baseline looked at the endings independently. 
%Then you can add the benchmark text below, and conclude that this indicates that this task is well designed and hard and the one hand, but might also point to potential disagreements between the train and the test data, which we highlight in this paper.}

@@

\paragraph{Neural Language Model.}
%~\ms{This needs to be placed somewhere else LOL}
%~\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}
%\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good. What I'm missing here are (a) an introductory 1-2  sentences to what are we doing here (I realize that it is not 100\% clear from the intro what is the role of these experiments other than showing that we have STOA results, so this can come later\\
%(b) A one-sentence description of your model. Currently, there is no clear separation between the model (RNN using LSTM) and the technical details. 
%Some general description of the model, and specifically the motivation behind (nothing fancy, just saying that we applied state-of-the-art LM tools, 
%which resemble the tools the authors had in mind when they designed the task).}

We investigate whether our model can benefit from state-of-the-art text comprehension models, for which this task was designed. Specifically, we train a recurrent language model (RLM) \cite{mikolov2010recurrent}. % , which have been shown to help
Unlike the model in this paper, which only considers the story endings, this language model harnesses the ROC Stories training set as intended by the authors, which consists of unsupervised, single-ending stories. Adding in the features from the language model further boosts our performance on the Story Cloze task.

% To leverage the genre of these short stories,\roy{Not sure this is the best introductory sentence, but you can leave it to me if you can't find anything better} we train a recurrent language model (RLM) \cite{mikolov2010recurrent},\roy{don't start with the details, but with the high level. We wanted wether our model can be combined with state-of-the-art text comprehension models, for which this task was designed. {\bf Specifically}, we train an RLM \dots}  which are used to achieve state-of-the-art performance on various tasks (e.g. machine translation)\roy{citation required}. 
%Training this RLM on the ROC stories, we harness the unsupervised, single-ended stories\roy{I would frame it differently. Unlike the model suggested in this paper, which only considers the endings, this model harnesses the training set as intended by the authors, which is composed of unsupervised, single-ended stories}, which boosts performance on the Story Cloze task.\roy{In what sense does it boost performance? we get STOA results without it...}

@@

% Eval
On its own, our neural language model performs moderately on the Story Cloze test. As hinted at by the creators of this task, simple language models aren't enough to do well. In fact, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55.0\%$ accuracy. When using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, we obtain $68.1\%$ (see \tabref{cloze_results}).

We notice that these features boosts perfromance by $3.6\%$, indicating that harnessing the unsupervised data from the ROC Stories complements using stylistic differences in the two endings in the Story Cloze stories.
% \roy{Now you need to discuss our results and what they mean. You can point to \tabref{cloze_results}}

% \roy{no, this is not why we include these as features (at least not in this paper:). It's because we want to see whether the different approaches are complementary.}
